Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex
finish editing ux section

\subsubsection{Fighting Mac's Security Features}
The biggest usability obstacle was the result of tensions between Mac's Gatekeeper 
code-signing feature on OS X, which prevents users from opening unsigned code 
downloaded from the Internet to execute on their machine unless overridden through
managing system preferences. Surprisingly, the feature which impacted Tor's usability
the most was the tension between a security precaution, and Tor's decision to self-sign
their downloads, rather than a specific feature of the Tor Browser itself. We found that 
encountering the Gatekeeper will cause frustration to most users, and may be enough 
to stop our participants in the download process:

>>>>

\subsubsection{Fighting Mac's Security Features}
The biggest usability obstacle was the result of tensions between Mac's Gatekeeper 
code-signing feature on OS X, which prevents users from opening unsigned code 
downloaded from the Internet to execute on their machine unless overridden through
managing system preferences. Participants could not download Tor without correctly
configuring these system preferences. We found that 
encountering the Gatekeeper will cause frustration to most users, and may be enough 
to stop our participants in the download process:
